### 2019-02-20 sections/intuition.tex
remove parens in breakfast example
make parameters italic
use `haveBreakfast`
add stub for abstract example

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Unit =
%     \makeDrink . \makeFood . makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink . \makeFood . makeDrink <&> makeFood
  let main : Task Unit =
    (makeBreakfast (makeTea <?> makeCoffee) makeEgg) >>? \<<d, f>>. eat d f
\end{TASK}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink . \makeFood . makeDrink <&> makeFood
%   let main : Task Unit =
%     (makeBreakfast (makeTea <?> makeCoffee) makeEgg) >>? \breakfast. eat breakfast
% \end{TASK}

@@

The step combinators give rise to a form of internal communication:
They represent data flow that \emph{follows} control flow.
\fixme{example with paper deadline}

@@

>>>>

\lstset{emph={makeDrink,makeFood}}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Unit =
%     \makeDrink. \makeFood. makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink. \makeFood. makeDrink <&> makeFood
  let main : Task Unit =
    makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? haveBreakfast
\end{TASK}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink. \makeFood. makeDrink <&> makeFood
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? \breakfast. eat breakfast
% \end{TASK}

@@

The step combinators give rise to a form of internal communication:
They represent data flow that \emph{follows} control flow.

@@

\lstset{emph={text}}
\begin{example}[Abstract submission]
\label{exm:abstract}

The task of writing an abstract for a conference is never done.
\fixme{Extend}

% \begin{TASK}
%   let submit : String -> Task Unit =
%     \text. delay 30 (sendTo "icfp19@sigplan.org" text)
%   let write : Task Unit =
%     edit "Abstract: ..." >>= \abstract. if 500 <= words abstract <= 700 then submit abstract else fail
% \end{TASK}

\begin{TASK}
  let submit : Ref String -> Task String = \text. sendTo "icfp19@sigplan.org" text
  let write : Ref String -> Task String = \text. update text
  let main : Task String = write abstract <|> delay 30 (submit abstract)
\end{TASK}

The \TS{delay} task is specified in Example~\ref{exm:delay} in Section~\ref{sec:language}.
